### 2023-12-20 draft_jss/draft_jss.Rmd
update draft

Table \@ref(tab:performance) shows the performance on the test set. Best model according to all metrics was RC with common input scaling and connection between input and output layers. Having one input scaling per feature did not improve the model which might be due to low generalisability of the hyperparameter of the training set to the test set due to non-stationarity. Additionaly, connecting input layer to output layer improved the model forecast.

We observe that elastic-net did not perform well and stayed close to the baseline prediction. However, when the penalisation is updated each day, the peformance improve. This is emphasize the problem of the transferrability of the hyperparameters to which multiple input scaling models seem more sensitive as they have more hyperparameters.

@@

>>>>

Table \@ref(tab:performance) shows the performance on the test set. Best model according to all metrics was RC with common input scaling and connection between input and output layers. Having one input scaling per feature did not improve the model which might be due to low generalisability of the hyperparameter of the training set to the test set due to non-stationarity. Additionaly, connecting input layer to output layer improved the model forecast. All RC models performed better than the elastic-net model.

@@

### Input feature importance

We compared the coefficients of the output layer estimated for the input layer and the reservoir nodes. Additionally, we compared the coefficient given to the input layer by the output layer in the reservoir and the coefficient estimated by the elastic-net model.

Figure \@ref{fig:importanceReservoir} illustrates the ranking of input layer compared to all connections to the output layer, including the 500 reservoir nodes and the 16 features of the input layer (excluding bias). The figure shows that the model with common input scaling tends to assign less weight to input layer compared to the model with multiple input scaling. This suggests that the reservoir with common input scaling provides more information than the reservoir with multiple input scaling, which aligns with its better performance, as shown in Table \@ref{tab:performance}.

```{r importanceReservoir, fig.cap="Mean feature importance of the 40 best hyperparameter sets by model, focus on the connection between the input and output layers. Models with direct connection between input and output layer are included. The rank is obtained by comparing the feature input layer and all other connection coefficients (both input and reservoir corresponding coefficients) attributed by the output layer at each date for each hyperparameter set. The higher the output layer's coefficient for the input layer, the closer its rank will be to 1 and the more important the feature is.", fig.height=6}
ls_use_case$plot_reservoir_importance
```

Furthermore, Figure \@ref{fig:importanceReservoirvsEnet} compares the coefficients assigned to input features by the elastic-net model and the RC models. While the coefficients are generally consistent across RC models, there are some notable differences with elastic-net. Specifically, certain features deemed important by the elastic-net model, such as the derivative of RT-PCR, and the derivative of Vaccine, are less important for the reservoir computing model. This may indicate that these features predictive ability is better conveyed by their relationship with other features, which is captured by the reservoir computing model but might not be by the elastic-net model. Conversely, emergency, IPTCC, proportion of positive RT-PCR, and hospitalizations are more important for the reservoir computing model than for the elastic-net model.

```{r importanceReservoirvsEnet, fig.cap="Mean feature coefficient of the 40 best hyperparameter sets by model and the elastic-net model. Only models with direct connection between input and output layer are included. The coefficients were calculated as the average value across all dates for each feature, model and hyperparamet set.", fig.height=6}
ls_use_case$plot_importance
```
